\Large \bf \projtitle

### 2015-05-05 doc/paper/paper.tex
added paper skeleton
Fix usepackage deps
added html5 localstorage to future work
assigning sections
adjusting assignments
Add diagram

\usepackage{style, verbatim, url}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\usepackage{cleveref}
\usepackage{breakurl}

@@

@@

\title{\Large \bf Zauberfl\"{o}te: A Transparent Peer-to-Peer CDN}

@@

\maketitle

\thispagestyle{empty}

\begin{abstract}
    % TODO
\end{abstract}

>>>>

\usepackage{style, verbatim, url, graphicx}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\usepackage{cleveref, breakurl}

@@

\newcommand{\zbf}{Zauberfl\"{o}te}
\newcommand{\projtitle}{\zbf: A Transparent Peer-to-Peer CDN}

@@

\title{\Large \bf \projtitle}

@@

\maketitle
\thispagestyle{empty}

\begin{abstract}

\end{abstract}

\section{Introduction}

% TODO Ankush

\section{\zbf\ API}

% TODO Ankush

\section{Implementation}

\begin{figure}
    \begin{centering}
        \includegraphics[width=.8\linewidth]{components.eps}
        \caption{Relationship between different components of the \zbf
        peer-to-peer download service.}
        \label{fig:components}
    \end{centering}
\end{figure}

\subsection{Connection manager}

% Anish

\subsection{Download manager}

% Anish

\subsubsection{Chunking}

\zbf\ divides assets into chunks; chunks are individually requested and sent between peers. We use a standard chunk size of 10240 bytes in our implementation; preliminary tests showed this chunk size to be reasonable. When a client asks for a resource, the download manager for that client determines the number of chunks for that resource from the specified size. The download manager then evenly distributes requests for these chunks among the peers with the resource.

\subsubsection{Hash validation}

% Anish

\subsubsection{Parallelization}

% Anish

\subsubsection{Fault tolerance}

% Anish

\subsection{Tracker interface}

% Katie

\subsection{Signaling channel}

% Katie

\subsection{DOM injection layer}

% Ankush

\section{Evaluation}

% TODO

\section{Future work}

\subsection{Per-chunk hash validation}

% Ankush

\subsection{Hybrid downloads over HTTP and P2P}

% Ankush

\subsection{Variable request sizes}

% Katie

\subsection{Bandwidth detection and prioritization}

% Katie

\subsection{Support for HTML5 media}

% Ankush

\section{Conclusions}

% TODO
